%\documentclass[a4paper,10pt]{article}
\documentclass[acmcsur,acmnow]{acmtrans2m}
%\documentclass[acmtocl,acmnow]{acmtrans2m}

%\acmVolume{V}
%\acmNumber{N}
%\acmYear{YY}
%\acmMonth{Month}

% packages
\usepackage[utf-8]{inputenc}
\usepackage{paralist}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{color,soul}
\usepackage{longtable}
\usepackage{wasysym}
\usepackage{pdflscape}
%\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{patterns}
\usepackage{url}

% definitions
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newdef{definition}[theorem]{Definition}
\newdef{remark}[theorem]{Remark}

\newcommand{\p}{\emph{P2P}}


%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{definition}[theorem]{Definition}

%\textwidth      6.5in
%\textheight     9.2in
%\oddsidemargin  -0.5cm
%\evensidemargin -0.5cm
%\parindent      0pt              
%\topmargin      -0.3in
%\headsep        20pt
%
%\parskip        5pt
%\parindent      10pt

\markboth{}{}{}

\title{Alleviating the Topology Mismatch Problem in Distributed Overlay Networks}

\author{
VASSILIS S. MOUSTAKAS$^1$, H\"USEYIN AKCAN$^2$, MEMA ROUSSOPOULOS$^1$ and ALEX
DELIS$^1$\\
$^1$\emph{University of Athens}, \emph{Athens}, \emph{Greece}\\
$^2$\emph{Izmir University of Economics}, \emph{Izmir}, \emph{Turkey}
}

\begin{abstract}
\emph{Peer-to-peer} (\p) systems have enjoyed immense attention and have been
widely deployed on the Internet for well over a decade.  %% no commas here
They are implemented via an overlay network abstraction, on top 
of the best-effort IP infrastructure of the Internet. 
\p\ systems offer a plethora of desirable features to 
distributed applications that are built on top of them including
anonymity, high availability and robustness, 
load balancing, quality of service, scalability, to name just a few.
Unfortunately, inherent weaknesses of \p\ systems, prevented 
applications from leveraging these features.
One major weakness, identified early on, is the \emph{topology mismatch problem}
between the overlay network and the underlying IP topology.
This mismatch can impose an extraordinary amount of unnecessary stress on
network resources and can adversely affect the scalability and efficiency of
applications built atop.
In this paper, we survey over a decade's worth of research efforts
aimed at alleviating the topology mismatch problem, in both unstructured
and structured \p\ systems.   
We provide a fine-grained categorization of the
suggested solutions and discuss the novelty as well as 
the  advantages and disadvantages of each such proposal.
Finally, we provide an analysis as well as pictorial comparisons 
of the reviewed approaches, since we aim to offer a comprehensive
reference for developers, system architects and researchers in the field.

\end{abstract}

\category{A.1}{General Literature}{Introductory and Survey}
\category{C.2.4}{Distributed Systems}{Distributed Applications}

\terms{Topology mismatch}

\keywords{Distributed systems, peer-to-peer architectures, overlay network,
topology awareness}

\begin{document}

\begin{bottomstuff}
Authors' addresses: Deprt. of Informatics and Telecommunications,
University of Athens, Athens, Greece. Deprt. of Software
Engineering, Izmir University of Economics, Izmir, Turkey.\\
emails: \{vsmoustakas,mema,ad\}@di.uoa.gr, huseyin.akcan@ieu.edu.tr
\end{bottomstuff}

\maketitle

\input{intro}
\input{background}

% \item Proximity Neighbor Selection\\
%Finally, the third approach, constructs the routing tables using proximity
%knowledge. Tapestry and Pastry's mechanisms of routing table
%maintenance try to minimize the distance to nodes appearing in a peer's routing
%table. Since routing is based on longest node ID prefix match, messages 
%are gradually forwarded to nearby nodes at each routing step.
%\cite{castro_proximityp2p_2002} argues on how Pastry exploits proximity
%neighbor selection in order to create a scheme that is (more) location-aware
%compared to the other well-known DHTs (CAN, Chord).
%
%\end{itemize}
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria: based on which protocol (eg Gnutella, CAN etc), peer
%selection (topology selection, cluster, cache etc), supports dynamic update,
%runtimes}}
%%\textbf{Algorithm} & \textbf{Overlay structure} & \textbf{Forwarding} &
%\textbf{Cache} & \textbf{Overlay optimization} & \textbf{Proximity information}
%& \textbf{Base protocol} & \textbf{Dynamic update} & \textbf{Runtime} \\
%
%
%{\sethlcolor{yellow}\hl{
%HA: Possible criteria2: Overlay optimization structure, base protocol (eg
%Gnutella, CAN etc), dynamic update, runtimes, scalability}}
%
%{\sethlcolor{yellow}\hl{
%HA: maybe add also the year of publication, and see if there is a pattern in
%terms of the method and the year??}}

\input{unstructured}

\input{structured}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: SOME INFORMATION ON ISP-ASSISTED TOPOLOGY AWARENESS
%       ATTENTION: NEEDS REWORDING
%
% P4P [16],instead, aimed to provide a general framework for P2P
%applications by developing ISP-application interfaces so that
%application software can use the network layer information,
%such as congestion status and network topology, for better
%performance and resource utilization.

%P4P [37] project attempts to address
%the problem through custom trackers, both for ISPs and P2P
%systems, using an interface based on a primal-dual decomposition
%of an optimization problem. This interface design simplifies
%the realization of traffic-engineering objectives from each parties’
%perspective and ensures the extensibility of the approach. Through
%simulation-based studies and limited experimental deployments,
%these collaborative approaches have been shown to effectively
%reduce network costs while minimally impacting application performance.
%A clear advantage of these proposals is that they
%allow ISPs to incorporate aggregated traffic policies in their tracker
%recommendations (e.g., a particular traffic balance ratio between
%peering providers). However, all of them require deployments
%of oracles for each participating ISP and their effectiveness is
%ultimately predicated on their adoption by P2P applications and a
%trust relationship between P2P users and their ISPs.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{acmtrans}
\bibliography{mard-survey}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{received}
Received Month Year;
revised Month Year; accepted Month Year
\end{received}

\end{document}
